---
title: "DataFest 2019"
author: "Hannah Snell"
date: "3/29/2019"
output:
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
require(knitr)
opts_chunk$set(
  tidy=TRUE,                    
  size="small",                   
  tidy.opts=list(width.cutoff=65), 
  fig.width=7, fig.height=5          
  )

require(mosaic)
require(tidyverse)
require(magrittr)
require(ggplot2)
library(readr)
library(lubridate)

```

```{r}
games <- read_csv("games.csv")
gps <- read_csv("gps.csv")
wellness <- read_csv("wellness.csv")
rpe <- read_csv("rpe.csv")
```


### DataFest 2019 

```{r}
gps_filtered <- gps %>% 
  select(GameID, PlayerID, GameClock, Speed, AccelLoad) %>% 
  filter(GameID %in% c(1, 7, 13, 18, 23, 29, 35)) %>% 
  group_by(GameClock, PlayerID, GameID) %>% 
  mutate(avgspeed = mean(Speed))

wellness_filtered <- wellness %>% 
  select(PlayerID, Fatigue, Soreness, SleepQuality, Illness, Menstruation, Date, USG) %>% 
  mutate(datenum = as.numeric(Date)) %>% 
  filter(datenum %in% c(17500, 17557, 17634, 17642, 17663, 17690, 17732)) %>% 
  select(- datenum)

games_filtered <- games %>% 
  select(Tournament, GameID, Date, Team, Outcome, Date) 
# %>% 
#   filter(GameID %in% c(1, 7, 13, 18, 23, 29, 35))
```


## Merge data from mutiple dataframes

```{r}
working <- merge(gps_filtered, wellness_filtered, "PlayerID")
workingdata <- working %>% 
  right_join(games_filtered, by = c("GameID", "Date")) %>% 
  group_by(PlayerID, GameID) %>% 
  filter(PlayerID %in% 0:16) %>% 
  select(- Speed, - AccelLoad, - Team)

```

## Sample Plot 

```{r}
set.seed(345)
sample_gps <- gps_filtered %>%
  ungroup() %>%
  sample_n(1000)

plot(sample_gps$GameClock, sample_gps$Speed)
```

## Fitting a test SLR for average speed of player vs. time on Game Clock for the first of each game in each tournament

```{r}
lm_gps <- lm(avgspeed ~ GameClock, data = single_gps_new)
ggplot(single_gps_new, aes(x = GameClock, y = avgspeed)) + geom_point() + facet_wrap(~PlayerID) + geom_jitter()
```

## Player 1 Models 

```{r}
# EDA for Player 1 

# Avg Speed per Game, Game 13

player1speedgame <- workingdata %>% 
  filter(GameID %in% 13)

speed_game <- lm(avgspeed ~ GameClock, player1speedgame)

ggplot(player1speedgame, aes(x = GameClock, y = avgspeed, color = Menstruation)) + 
  geom_point() + 
  geom_jitter() + 
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~PlayerID)

summary(speed_game)
```

According to the summary statistics, the slope is significant (p < 0.05). This means that for Player 1 in Game 13, there is an average associated increase of 1.337x10^-3 units of fatigue per second of play. 

# USELESS CODE AND NOTES STARTING FROM HERE 

## Function to find each player's average speed

```{r}
trying_out <- function(num) {
  player <- workingdata %>% 
    filter(PlayerID %in% num)
  
  playerspeedgame <- player %>% 
    filter(GameID %in% 13)

  speed_game <- lm(avgspeed ~ GameClock, playerspeedgame)
  
  speed_game %>% filter(!is.na(avgspeed))

  ggplot(playerspeedgame, aes(x = GameClock, y = avgspeed)) + 
    geom_point() + 
    geom_jitter() + 
    geom_smooth(method = "lm", se = FALSE) 
}
  
```

## Players mapping 

```{r}
list_nums <- c("1", "2", "3", "4")
map(list_nums, trying_out)
```

```{r}
list_nums2 <- c("5", "6", "7", "8")
map(list_nums2, trying_out)
```

```{r}
list_nums3 <- c("9", "10", "11", "12")
map(list_nums3, trying_out)
```


```{r}
list_nums4 <- c("13", "14", "15", "16")
map(list_nums4, trying_out)
```

## Does menstruation effect USG? No.

```{r}
ggplot(workingdata, aes(x = GameID, y = Fatigue)) + geom_bar(stat = "identity") + facet_wrap(~PlayerID)

```

USG ranges from 1.002 to 1,0035
Could have a condition that makes me thirsty quickly or opposite -> requires further testing

game time versus speed and menstruation 
player id and usg and menstruation 

```{r}
well <- wellness_filtered %>% 
  filter(!is.na(USG))

ggplot(well, aes(x = Date, y = USG, color = Menstruation)) +
  facet_wrap(~PlayerID) +
  geom_jitter() + 
  ylim(1, 1.05)
```

```{r}
ggplot(wellness, aes(x=MonitoringScore)) +
  geom_bar()

ggplot(wellness, aes(x=SleepQuality)) +
  geom_bar()

ggplot(wellness, aes(x=Illness)) +
  geom_bar()

new_ll <- wellness %>% arrange(desc(TrainingReadiness))

ggplot(new_ll, aes(x=TrainingReadiness)) +
  geom_bar()

ggplot(wellness, aes(x=MonitoringScore, y=Fatigue)) +
  geom_point()
```

******* 








